\documentclass[11pt]{article}

% --- Packages ---
\usepackage[margin=0.75in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{multicol}
\usepackage{titlesec} 
\usepackage{enumitem} 
\usepackage[en-US]{datetime2} 
\usepackage[T1]{fontenc}
\DTMlangsetup{showdayofmonth=true}

% --- Section Formatting ---
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3ex}{1.5ex}

\setlength{\parindent}{0pt}

\begin{document}
\pagestyle{empty} 

% --- Header ---
\begin{center}
    {\Huge \textbf{James Chubbuck}} \\[1.5ex]
    Stanford, CA $\vert$ \href{mailto:chubbuck@stanford.edu}{chubbuck@stanford.edu} \\[1ex]
    \textit{\today}
\end{center}

\vspace{2ex}

% --- Education ---
\section*{Education}

\textbf{Stanford University} \hfill \textit{Class of 2029} \\
Prospective engineering physics major and classics minor. 

\vspace{1.5ex}

\textbf{Hun School of Princeton} \hfill \textit{Class of 2025} \\
4.0 GPA $\vert$ 1530 SAT \\
Notable classes: AP Calculus BC, Multivariable Calculus, Linear Algebra, AP Statistics, AP Physics C: Mechanics, AP Latin, Computer Aided Design.

% --- Recognitions and Awards ---
\section*{Recognitions and Awards}
\begin{itemize}[leftmargin=*, nosep, itemsep=0.3ex]
  \item American String Teachers Association Certificate Advancement Program Violin Level 10 (2024)
  \item College Board AP Scholar Award (2024)
  \item College Board National Indigenous Recognition Program (2024)
  \item National Cum Laude Society (2024)
  \item National Honor Society, John Gale Hun Chapter (2023)
  \item National Latin Exam Medalist (2022--2024)
\end{itemize}

% --- Certifications ---
\section*{Certifications}

\text{ASHI Wilderness First Aid} \hfill \textit{Valid through 2027}

\vspace{1.5ex}

\text{Lifeguarding (with Deep Water), CPR/AED, and First Aid} \hfill \textit{Valid through 2027}

% --- Work Experience and Volunteering ---
\section*{Work Experience and Volunteering}

\textbf{East Coast Cherokees} \hfill \textit{2023--Present} \\
Founding member of an official Cherokee Nation 501(c)(3) satellite community for At-Large Citizens in New York, New Jersey, Pennsylvania, and Delaware. Developed initial website. 

\vspace{1.5ex}

\textbf{Camp Counselor} \hfill \textit{2023--2025} \\
Counselor at a sleepaway camp in Maine for boys aged seven to fifteen. Assisted with camp activities and camping trips. 

\vspace{1.5ex}

\textbf{SAT Tutoring} \hfill \textit{2024} \\
Volunteered tutoring peers in preparation for the March 2024 SAT.

\vspace{1.5ex}

\textbf{New York Botanical Garden} \hfill \textit{2022--2023} \\
Volunteered for Urban Advantage Family programs.

% --- Programming Languages ---
\section*{Programming Languages}
\setlength{\multicolsep}{0.5ex}
\begin{multicols}{3}
\begin{itemize}[leftmargin=*, nosep]
  \item HTML/CSS
  \item JS/TS
  \item Java
  \item Nix
  \item Python
  \item TI-BASIC
\end{itemize}
\end{multicols}

% --- Recent Projects ---
\section*{Recent Projects}

\textbf{Diachronic Linguistics Analysis} \hfill \textit{Ongoing} \\
Developing a Python-based tool utilizing embedding models and phonetic similarity algorithms to identify semantically and phonetically similar Greek words with disparate etymological roots to study language evolution.

\vspace{1.5ex}

\textbf{Lightweight JavaScript Framework} \hfill \textit{2024} \\
Wrote a $\sim$0.5kB JavaScript framework which provides basic component functionality, including nesting, able to pass arbitrary parameters to components.

\vspace{1.5ex}

\textbf{Numerical OCR} \hfill \textit{2024} \\
Enlisted the help of many friends to build a large dataset of handwritten numerals, then used Python to train a simple model to recognize digits. 

\vspace{1.5ex}

\textbf{VPS} \hfill \textit{Ongoing} \\
Actively maintain a virtual private server that runs several applications, such as Matrix, RSS aggregators, and other services.

\vspace{1.5ex}

\textbf{Framework OCuLink Module} \hfill \textit{2023} \\
Used off-the-shelf hardware to fabricate an OCuLink module for use in Framework laptop expansion bays. 

\vspace{1.5ex}

\textbf{Electronics Repair} \hfill \textit{Ongoing} \\
Repaired a number of broken electronics, such as motherboards, laptops, and a drone used in high school demonstrations. 

\end{document}
